---
title: "Summary of Coded Surveys on Psychology Researcher Behavior"
author: "Hannah Moshontz"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
editor_options: 
  chunk_output_type: console
---

This markdown provides an overview of articles evaluted for inclusion in the RRR Project 6 synthesis of psychology researcher behavior change.

The literature evaluated here were identified by overlapping searches:


* Forward search on John et al	use of QRP in Google Scholar
* Replicated the search strategy in Stricker & Gunther (2019) 
* Google Scholar forward search on Broome	et al. (2005)
* PsychInfo title and abstract search for "questionable research practices" AND psycholog*
* PsychInfo title search for "open data" AND psycholog*	open data
* PsychInfo title search for "open materials" AND psycholog*	open materials
* PsychInfo title search for "open code" AND psycholog*	open code
* Zotero folder from OSF on surveys of open science behaviors
* Backwards searches on included articles and meta-science papers
* Twitter post asking about published and unpublished behavior surveys on ether qrp or os behaviors

Studies were evaluated for inclusion if the title and abstract suggested that the survey may have:

* asked psychologists about their own past use of QRP or open science behaviors

Studies were included if they:

* estimated or shared data that allowed for the estimate of rates among psychologists using original data
* asked about at least one of the 10 QRPs evaluated by John et al. or about sharing data, code, or materials

Studies were coded by Hannah Moshontz, Laura Scherer, or Joe Hilgard. The values for self-report estimates, effective date, and any value that required inference were confirmed in a group meeting.

## Set up
```{r, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(tidyverse)
library(janitor)
library(gsheet)
library(kableExtra)
library(lubridate)
```

## Import codes from google sheet
```{r, warning = FALSE, message = FALSE}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1fY6gPYEY3283W3RPT1u5DmMwuAc-mFZoDdfUb4vcvEI/edit#gid=0") %>%
  write_csv("behavior_survey_codes.csv")

behavior_survey_codes <- read_csv("./behavior_survey_codes.csv") %>%
  clean_names("snake") %>%
  slice(-1) %>%
  glimpse()
```

## Describe the initial evaluation

### Article relevance to quantitative summary
```{r}
behavior_survey_codes %>%
  tabyl(relevant)
```

### Publication Years: yes and maybe articles
```{r}
behavior_survey_codes %>% 
  filter(relevant != "no") %>% 
  tabyl(publication_year, show_na = TRUE)
```

### Notes about relevance: yes articles
```{r}
behavior_survey_codes %>% 
  filter(relevant == "yes") %>% 
  select(first_author, relevant_reason) %>% 
  kable() %>% 
  kable_styling()
```

### Notes about relevance: maybe articles
```{r}
behavior_survey_codes %>% 
  filter(relevant == "maybe") %>% 
  select(first_author, relevant_reason) %>% 
  kable() %>% 
  kable_styling()
```

### Notes about relevance: no articles
```{r}
behavior_survey_codes %>% 
  filter(relevant == "no") %>% 
  select(first_author, relevant_reason) %>% 
  kable() %>% 
  kable_styling()
```

## Describe the final evaluation

```{r}
behavior_estimates <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1fY6gPYEY3283W3RPT1u5DmMwuAc-mFZoDdfUb4vcvEI/edit#gid=1789844879") %>% 
  slice(-1) %>% 
  clean_names("snake") %>% 
  mutate(across(everything(), ~str_replace(.x, "^na$", ""))) %>% #replace "na" with null
    mutate(across(everything(), ~str_replace(.x, "^NA$", ""))) %>% #replace "NA" with null
    mutate(across(everything(), ~str_replace(.x, "^unknown$", ""))) %>% #replace "unknown" with null
  mutate(across(contains("date"), mdy)) %>% 
  glimpse()
```

There are `r nrow(behavior_estimates)` samples from `r length(unique(behavior_estimates$first_author))` publications.

### Target populations and samples

```{r}
behavior_estimates %>% 
  select(first_author, effective_date, target_population, sample) %>% 
  distinct() %>% 
  kable() %>% 
  kable_styling()
```

### Effective date

Given survey frame & question wording, the most current actual effective date (yyyy/mm/dd) for use in plots, etc. If a day wasn't specified, the last day of the specified month was used. If no end date of the survey was reported, the submission date of the article was used, or the publication date if the submission date was not listed.

```{r}
behavior_estimates %>% 
  mutate(effective_date = year(effective_date)) %>% 
  tabyl(effective_date)
```

### Inferences made in extracting estimates

```{r}
behavior_estimates %>% 
  filter(inferences_made != "no") %>% 
  select(first_author, inferences_made) %>% 
  kable() %>% 
  kable_styling()
```


### Whether the estimates are relevant to undermining replicability (QRP) or supporting it (OS)

```{r}
behavior_estimates %>% 
  tabyl(type_os_qrp)
```

### Whether the estimates are from self-report or from audits

```{r}
behavior_estimates %>% 
  tabyl(type_sr_audit)
```

### QRP: question stems and response options

```{r}
behavior_estimates %>% 
  filter(type_os_qrp == "qrp") %>% 
  group_by(question_stem, response_options) %>% 
  summarize(n_samples = n(),
            papers = paste0(unique(first_author), collapse = ",")) %>% 
  select(n_samples, papers, everything()) %>% 
  arrange(-n_samples) %>% 
  kable() %>% 
  kable_styling()
```

#### QRP extracted estimate type

```{r}
behavior_estimates %>% 
  filter(type_os_qrp == "qrp") %>% 
  tabyl(estimate_type)
```


### OS: question stems and response options

```{r}
behavior_estimates %>% 
  filter(type_os_qrp == "os") %>% 
  select(question_stem, response_options) %>% 
  distinct() %>% 
  kable() %>% 
  kable_styling()
```

#### OS extracted estimate type

```{r}
behavior_estimates %>% 
  filter(type_os_qrp == "os") %>% 
  tabyl(estimate_type)
```



