---
title: "Summary of estimates of QRP/OS behaviors among psychologists"
author: "Hannah Moshontz"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Setup

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(gsheet)
library(lubridate)
library(kableExtra)
library(psych)
```

Import and glimpse
```{r}
behavior_estimates <- gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1fY6gPYEY3283W3RPT1u5DmMwuAc-mFZoDdfUb4vcvEI/edit#gid=1789844879") %>% 
  slice(-1) %>% #drop explanatory row on coding sheet
  clean_names("snake") %>% #variables to snake case
  mutate(across(everything(), ~str_replace(.x, "^na$", ""))) %>% #replace "na" with null
    mutate(across(everything(), ~str_replace(.x, "^NA$", ""))) %>% #replace "NA" with null
    mutate(across(everything(), ~str_replace(.x, "^unknown$", ""))) %>% #replace "unknown" with null
  mutate(across(contains("date"), mdy)) %>% #parse date as a date
  glimpse() 
```

### Behaviors that undermine replicability (qrp behaviors): self-report table

Get information to include in the table.
```{r}
qrp_summary <- behavior_estimates %>% 
  filter(type_os_qrp == "qrp",
         type_sr_audit == "sr") %>% 
  select(-general_qrp) %>% 
  select(first_author,
         effective_date,
         n,
         psych_area,
         target_population,
         subgroup,
         important_notes,
         estimate_type,
         any_qrp:falsified) %>% 
  arrange(effective_date) %>% 
  mutate(effective_date = year(effective_date)) 
```

Calculate min, median, max.
```{r}
qrp_summary_descriptives <- qrp_summary %>% 
  select(any_qrp:falsified) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  describe(na.rm = TRUE) %>% 
  select(min, median, max) %>% 
  t() %>% #transpose
  as_tibble() #make matrix a tibble

qrp_summary_descriptives <- qrp_summary_descriptives %>% 
  mutate(first_author = c("min", "median", "max")) %>%
  mutate(across(everything(), as.character))
```

Calculate weighted averages.
```{r}
weighted_mean <- qrp_summary %>% 
  select(n, any_qrp:falsified) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  summarize(across(-n,~weighted.mean(.x, n, na.rm = TRUE))) %>% 
  mutate(first_author = "weighted mean") %>%  
  mutate(across(everything(), as.character))
```

Create table, round values, save as csv.
```{r}
qrp_summary <- bind_rows(qrp_summary_descriptives, weighted_mean) %>%
  bind_rows(qrp_summary) %>% 
  select(first_author:estimate_type, everything()) %>%
  arrange(effective_date)

qrp_summary %>% 
  kable() %>% 
  kable_styling()

write_csv(qrp_summary, "qrp_estimates.csv")

read_csv("qrp_estimates.csv") %>% #reimporting to correctly parse numeric
  mutate(across(where(is.numeric), ~round(.x, 2))) %>% #round
  write_csv("qrp_estimates.csv") #rewrite csv

```


### Behaviors that promote replicability (open science behaviors): self-report table

Get information to include in the table.
```{r}
os_summary <- behavior_estimates %>% 
  filter(type_os_qrp == "os") %>% 
  filter(type_sr_audit == "sr") %>% 
  select(first_author,
         effective_date,
         n,
         psych_area,
         type_sr_audit,
         target_population,
         subgroup,
         important_notes,
         estimate_type,
         posted_data:preregistered) %>% 
  arrange(effective_date) %>% 
  mutate(effective_date = year(effective_date)) 
```

Calculate min, median, max.
```{r}
os_summary_descriptives <- os_summary %>% 
  select(posted_data:preregistered) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  describe(na.rm = TRUE) %>% 
  select(min, median, max) %>% 
  t() %>% 
  as_tibble()

os_summary_descriptives <- os_summary_descriptives %>% 
  mutate(first_author = c("min", "median", "max")) %>%
  mutate(across(everything(), as.character))
```

Calculate weighted averages.
```{r}
os_weighted_mean <- os_summary %>% 
  select(n, posted_data:preregistered) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  summarize(across(-n,~weighted.mean(.x, n, na.rm = TRUE))) %>% 
  mutate(first_author = "weighted mean") %>%  
  mutate(across(everything(), as.character))
```

Create table, round values, save as csv.
```{r}
os_summary <- bind_rows(os_summary_descriptives, os_weighted_mean) %>%
  bind_rows(os_summary) %>% 
  select(first_author:estimate_type, everything()) %>%
  arrange(effective_date)

os_summary %>% 
  kable() %>% 
  kable_styling()

write_csv(os_summary, "os_estimates.csv")

read_csv("os_estimates.csv") %>% #reimporting to correctly parse numeric
  mutate(across(where(is.numeric), ~round(.x, 2))) %>% #round
  write_csv("os_estimates.csv") #rewrite csv
```


### Behaviors that promote replicability (open science behaviors): audit table

Get information to include in the table.
```{r}
os_audit_summary <- behavior_estimates %>% 
  filter(type_os_qrp == "os") %>% 
  filter(type_sr_audit == "audit") %>% 
  select(first_author,
         effective_date,
         n,
         psych_area,
         type_sr_audit,
         target_population,
         subgroup,
         important_notes,
         estimate_type,
         posted_data:preregistered) %>% 
  arrange(effective_date) %>% 
  mutate(effective_date = year(effective_date)) 
```

Calculate min, median, max.
```{r}
os_audit_summary_descriptives <- os_audit_summary %>% 
  select(posted_data:preregistered) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  describe(na.rm = TRUE) %>% 
  select(min, median, max) %>% 
  t() %>% 
  as_tibble()

os_audit_summary_descriptives <- os_audit_summary_descriptives %>% 
  mutate(first_author = c("min", "median", "max")) %>%
  mutate(across(everything(), as.character))
```

Calculate weighted averages.
```{r}
os_audit_weighted_mean <- os_audit_summary %>% 
  select(n, posted_data:preregistered) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  summarize(across(-n,~weighted.mean(.x, n, na.rm = TRUE))) %>% 
  mutate(first_author = "weighted mean") %>%  
  mutate(across(everything(), as.character))
```

Create table, round values, save as csv.
```{r}
os_audit_summary <- bind_rows(
  os_audit_summary_descriptives, 
  os_audit_weighted_mean) %>%
  bind_rows(os_audit_summary) %>% 
  select(first_author:estimate_type, everything()) %>%
  arrange(effective_date)

os_audit_summary %>% 
  kable() %>% 
  kable_styling()

write_csv(os_audit_summary, "os_audit_estimates.csv")

read_csv("os_audit_estimates.csv") %>% #reimporting to correctly parse numeric
  mutate(across(where(is.numeric), ~round(.x, 2))) %>% #round
  write_csv("os_audit_estimates.csv") #rewrite csv
```


